---
title: "SABES Cost-Effectiveness Analysis"
author: "Blythe Adamson"
date: "8/16/2018"
output: 
  html_document:
    theme: yeti
    highlight: tango
    toc: true
    toc_float: true
---

__Date created:__ `r format(Sys.time(), '%d %B, %Y')`

__Project:__ The SABES Study

__Repository:__ https://github.com/blythejane/lima-hiv-testing

```{r global_options, include = FALSE}

knitr::opts_chunk$set(fig.width = 9,
                      fig.height = 4,
                      echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      tidy = FALSE)
```

```{r libraries}

library(ggplot2)
library(dplyr)
library(knitr)
library(rmarkdown)
library(htmlTable)
```

***
# Overview
***

The purpose of this analysis is to estimate the cost-effectiveness of the Sabes program compared 
to the standard of care from the perspective of the Peruvian Ministry of Health. We will evaluate 
the cost of a testing program that incorporates the Sabes strategy, the effectiveness of the program 
by estimating the proportion of cases of HIV detected during the acute/recent phase of infection, 
and the proportion of individuals with new HIV diagnoses successfully linked to care through the 
peer navigation program. This project will aid Peruvian policy makers in assessing the economic 
impact of implementing the Sabes approach of frequent HIV testing and rapid linkage to HIV care 
through the peer navigators. It provides evidence for decision makers as they decide whether 
or not to adopt this strategy.


### __Authors and affiliations__
Blythe J.S. Adamson, PhD, MPH [a,b,c], Angela Ulrich, PhD, MPH [b,d], Enrique M. Saldarriaga, MS [a], Robert De La Grecca [f,g], Daniel Wood, PhD [b], Joseph B. Babigumira, PhD, MS, MBChB [a,d], Jorge L. Sanchez, MD, MPH [g], Javier R. Lama, MD, MPH [h], Dobromir Dimitrov, PhD [b,e], Ann Duerr, MD, PhD [b,d]

a The Comparative Health Outcomes, Policy, & Economics (CHOICE) Institute, University of Washington, Seattle, WA, USA

b Vaccine and Infectious Disease Division, Fred Hutchinson Cancer Research Center, Seattle, WA

c Flatiron Health, New York, NY

d Department of Global Health, University of Washington, Seattle, WA, USA

e Department of Applied Mathematics, University of Washington, Seattle, WA, USA

f HIV Vaccine Trials Network, Fred Hutchinson Cancer Research Center, Seattle, WA, USA

g Centro de Investigaciones Tecnologicas Biomedicas y Medioambientales, Universidad Nacional Mayor de San Marcos, Lima, Perú

h Asociación Civil Impacta Salud y Educación, Lima, Perú


***
# Model
***

### Naming Conventions

`lima_` is the prefix for the dynamic trace

`trt` is an indicator for the scenario (includes ref, int, ref2, int2...)

`lima_trt` : generic data frame of dynamic output with "trt" representing either reference group 
("ref") or intervention group ("int")

`lima_ref` : reference group (control) in the base case analysis

`lima_int` : SABES intervention in the base case analysis

`lima_trt_ly` : trace with person-time in quarters, to sum for life years

`lima_trt_qaly` : trace with quarterly discounted qalys, to sum for total discounted qalys


```{r select_scenario, echo=FALSE}

main_analysis <- TRUE # if FALSE then runs with the base2 and int2 for sensitivity 
#                       analysis assuming an alternative HIV care cascade

# LOAD DYANAMIC MODEL SIMULATION OUTPUT
if(main_analysis){
  lima_ref <- read.csv("lima_base.csv")
  lima_int <- read.csv("lima_int.csv")
}else{
  lima_ref <- read.csv("lima_base2.csv")
  lima_int <- read.csv("lima_int2.csv")
}

cpi <- read.csv("cpi.csv") # consumer price index for peru
```


```{r population size, echo = FALSE}

# TIME HORIZON
t_start <- min(lima_ref$Time) # start year of simulations (calibration 2004-2014)
t_end <- max(lima_ref$Time) # end year of time horizon

# POPULATION SIZE  -------------------------------------------------------------

PopSize <- function(hiv_trt){
  hiv_trt <- hiv_trt[hiv_trt$Time >= 2018,]
  hiv_trt[,1] <- as.character(hiv_trt[,1])
  hiv_trt[,3] <- as.numeric(hiv_trt[,3])
  hiv_trt$AcuteDx <- NA
  hiv_trt$AcuteDx[1] <- 0
  hiv_trt$RegularDx <- NA
  hiv_trt$RegularDx[1] <- 0
  for(i in 2:81){
    hiv_trt$AcuteDx[i] <- hiv_trt$NewD1[i] - hiv_trt$NewD1[i-1]
    hiv_trt$RegularDx[i] <- rowSums(hiv_trt[i,58:61]) - rowSums(hiv_trt[c(i-1),58:61])
  }
  hiv_trt$popsize <- rowSums(hiv_trt[,3:54]) # sum the popsize at each time point
  hiv_trt$infected <- rowSums(hiv_trt[,5:54])
  hiv_trt$pAcuteInf <- (hiv_trt$I1L + hiv_trt$I1H)/hiv_trt$infected
  return(hiv_trt)
}

lima_ref <- PopSize(lima_ref)
lima_int <- PopSize(lima_int)

popsize_min <- min(lima_ref$popsize)
popsize_max <- max(lima_ref$popsize)

```

<br>

## Parameters

```{r params}

pp_n <- round(lima_ref$popsize[lima_ref$Time == 2018]) # denominator for per person totals

discount <- 0.03
threshold <- 6572 # 2017 GDP for Peru from World Bank

uAcute <- 0.690     # se: 0.058; unknown utility, assume same as <350
u500   <- 0.730     # se: 0.052 
u350   <- 0.710     # se: 0.059
u200   <- 0.690     # se: 0.058
uAIDS  <- 0.690     # se: 0.058
# Sources: Review by Whitham 2016 & CDC Report 16 2014 (CDC Medical Monitoring Project)

cAcuteDx <- 6412.42 # does acute infection have a cost? what is it?
  # calculated from Angie Ulrich TreeAge costing model on 4/13/18
  #To see if the model results are consistent with the trial, we simulated on a cohort size of 2,084.
  #The current model estimates the following:
  #  Incident cases: 259
  #Detected during acute HIV infection: 234 (90%)
  #Total Cost: $1,500,508
  #Cost per acute infection diagnosed: $6,412.42

        # cAcuteDx <- 23437.42 # one-way sensitivity analysis
```

The cost of an acute infection is assumed to be `r scales::dollar(cAcuteDx)` per additional 
infection diagnosed. We assume a cost-effectiveness threshold of `r scales::dollar(threshold)` per QALY gained 
(1xGDP per capita for Lima in 2017).

<br>


## Study Population

The dynamic transmission model begins in the year `r t_start` and ends in the year `r t_end`.
The calibration period takes place between the years 2004-2017, and these results are excluded from the analysis. The intervention period begins in 2018. 
The population size fluxuates between `r scales::comma(popsize_min, digits = 0)` - `r scales::comma(popsize_max, digits = 0)` people during these years. 

```{r describe study population}

TableDescribe <- function(hiv_ref, hiv_trt){
  
  Indicator <- c(
    "Population Size, 2018",
    'Population Size, 2038',
    "HIV Infections in 2018",
    "HIV Infections in 2038",
    "Incident Infections 2018-2038",
    "HIV Prevalence (%) in 2018",
    "HIV Prevalence (%) in 2038",
    "Acute Fraction of HIV (%) in 2018",
    "Acute Fraction of HIV (%) in 2038"
  )
  
  Reference <- c(
    round(hiv_ref$popsize[hiv_ref$Time == 2018]),
    round(hiv_ref$popsize[hiv_ref$Time == 2038]),
    round(hiv_ref$infected[hiv_ref$Time == 2018]),
    round(hiv_ref$infected[hiv_ref$Time == 2038]),
    round(hiv_ref$NewI[hiv_ref$Time == 2038]-hiv_ref$NewI[hiv_ref$Time == 2018]),
    round(hiv_ref$infected[hiv_ref$Time == 2018]/hiv_ref$popsize[hiv_ref$Time == 2018], digits = 3),
    round(hiv_ref$infected[hiv_ref$Time == 2038]/hiv_ref$popsize[hiv_ref$Time == 2038], digits = 3),
    round((hiv_ref$I1L[hiv_ref$Time == 2018]+hiv_ref$I1H[hiv_ref$Time == 2018])/hiv_ref$infected[hiv_ref$Time == 2018], digits = 3),
    round((hiv_ref$I1L[hiv_ref$Time == 2038]+hiv_ref$I1H[hiv_ref$Time == 2038])/hiv_ref$infected[hiv_ref$Time == 2038], digits = 3)
  )
  
  Intervention <- c(
    round(hiv_trt$popsize[hiv_trt$Time == 2018]),
    round(hiv_trt$popsize[hiv_trt$Time == 2038]),
    round(hiv_trt$infected[hiv_trt$Time == 2018]),
    round(hiv_trt$infected[hiv_trt$Time == 2038]),
    round(hiv_trt$NewI[hiv_ref$Time == 2038]-hiv_ref$NewI[hiv_trt$Time == 2018]),
    round(hiv_trt$infected[hiv_trt$Time == 2018]/hiv_trt$popsize[hiv_trt$Time == 2018], digits = 3),
    round(hiv_trt$infected[hiv_trt$Time == 2038]/hiv_trt$popsize[hiv_trt$Time == 2038], digits = 3),
    round((hiv_trt$I1L[hiv_trt$Time == 2018]+hiv_trt$I1H[hiv_trt$Time == 2018])/hiv_trt$infected[hiv_trt$Time == 2018], digits = 3),
    round((hiv_trt$I1L[hiv_trt$Time == 2038]+hiv_trt$I1H[hiv_trt$Time == 2038])/hiv_trt$infected[hiv_trt$Time == 2038], digits = 3)
  )
  
  table_describe <- as.data.frame(cbind(Indicator, Reference, Intervention))
  
}
table_describe <- TableDescribe(lima_ref, lima_int)

```

<br>

## Health States 

```{r health states}
# HEALTH STATES
state_names <- colnames(lima_ref[,3:56])

states_n <- n_distinct(state_names)

DefineStates <- function(state_names){
  # Define the attributes of each model health state for the cost-effectiveness analysis
  #
  # Args:
  #     @state_names: vector of character string short names for each health state in the model
  #
  # Returns:
  #     Table of health state names and corresponding HIV status, awareness, CD4-count, risk level, and ART use
  
  st <- data.frame(state_names)
  
  st$state <- as.character(st$state_names)
  
  # HIV infection status
  st$hiv[5:54] <- "infected"
  st$hiv[1:4] <- "susceptible"
  
  # phase of the HIV care cascade
  # I: Infected, D: Diagnosed, E: Enaged (not on ART), U: Unsuppressed and ON ART, T: Suppressed and on ART
  st$aware <- NA
  st$aware[1:4] <- "S"       # Susceptible
  st$aware[5:14] <- "I"      # Infected and unaware
  st$aware[15:24] <- "D"     # Diagnosed
  st$aware[25:34] <- "E"     # Enaged (not on ART)
  st$aware[35:44] <- "U"     # Unsuppressed and ON ART
  st$aware[45:54] <- "T"     # Suppressed and on ART
  aware_labels <- unique(st$aware)
  
  # CD4 Count of 1: ACUTE, 2: >500 CD4, 3: 350-500 CD4, 4: 200-350, 5: <200
  st$cd4_cat <- NA
  temp <- c(seq(5,54,10),seq(6,54,10))
  for(i in temp){
    st$cd4_cat[i] <- 1
    st$cd4[i] <- "Acute"
  }
  temp <- c(seq(7,54,10),seq(8,54,10))
  for(i in temp){
    st$cd4_cat[i] <- 2
    st$cd4[i] <- ">500"
  }
  temp <- c(seq(9,54,10),seq(10,54,10))
  for(i in temp){
    st$cd4_cat[i] <- 3
    st$cd4[i] <- "350-500"
  }
  temp <- c(seq(11,54,10),seq(12,54,10))
  for(i in temp){
    st$cd4_cat[i] <- 4
    st$cd4[i] <- "200-349"
  }
  temp <- c(seq(13,54,10),seq(14,54,10))
  for(i in temp){
    st$cd4_cat[i] <- 5
    st$cd4[i] <- "<200"
  }
  cd4_labels <- unique(st$cd4)
  
  # Risk level for low or high sexual activity
  st$risk <- NA
  temp <- c(seq(1,54,2)) # rows of low risk health states
  for(i in temp){
    st$risk[i] <- "low"
  }
  temp <- c(seq(2,54,2)) # rows of high risk health states
  for(i in temp){
    st$risk[i] <- "high"
  }
  
  # Treatment with ART
  st$art <- 0
  st$art[st$care == 'Susceptible'] <- NA
  st$art[st$aware=='U' | st$aware == 'T'] <- 1
  
  return(st)
}

states <- DefineStates(state_names)  # data frame with indicator variables

save(states, file = "states.rda")

aware_labels <- unique(na.omit(states$aware))

cd4_labels <- unique(na.omit(states$cd4))

UtilityWeights <- function(state){
  # Assign utility weights to each health state
  #
  # Args:
  #    @state: table of health state names and attributes
  #
  # Returns:
  #    Table of health states used in argument with added column that has utility value
  
  st <- state
  st$utility <- NA
  st$utility[st$hiv == 'susceptible'] <- 1
  st$utility[st$cd4 == 'Acute'] <- uAcute
  st$utility[st$cd4 == '>500'] <- u500
  st$utility[st$cd4 == '350-500'] <- u350
  st$utility[st$cd4 == '200-349'] <- u200
  st$utility[st$cd4 == '<200'] <- uAIDS
  st$utility[st$aware == "T"] <- u500
  return(st)
}

states <- UtilityWeights(states)
htmlTable(states)
```

<br>

***
# Results
***


## Epidemic Impact

Here we summarize the epidemic impact estimated by the dynamic tranmission model. 

```{r summary of dynamic results}
htmlTable(table_describe)
```


## Clinical Impact

```{r estimate clinical impact}
# FUNCTIONS FOR HEALTH OUTCOMES ------------------------------------------------------------

GetPersonTime <- function(hiv_trt){
  # Calculate the total population life years (LYs) in each health state for a given scenario
  #     during the analysis time horizon
  #
  # Args:
  #   @hiv_trt: table of life years in each heath state each quarter of analysis time horizon for a given scenario
  #
  # Returns: 
  #   Table of total population life years in each health state for each quarter of the analysis time horizon
  
  ly <- hiv_trt[hiv_trt$Time >= 2018,]
  
  ly[3:54] <- ly[3:54]/4
  
  ly$totalLY <- rowSums(ly[,3:54])
  
  ly$nyr <- trunc(ly$Time, digits = 0)
  
  ly$nyr <- ly$nyr - 2018
  
  return(ly)
}

GetQALYs <- function(hiv_trt_ly){
  # Calculate the discounted QALYs from life years (LYs)
  #
  # Args:
  #   @hiv_trt_ly: table of life years in each heath state each quarter of analysis time horizon for a given scenario
  #
  # Returns: 
  #   Table of discounted QALYs in each health state each quarter
  
  hiv_trt_qaly <- hiv_trt_ly
  
  hiv_trt_qaly[3:54] <- NA
  
  for(i in 1:nrow(hiv_trt_ly)){
    
    hiv_trt_qaly[i,3:54] <- hiv_trt_ly[i,3:54] * states$utility * (1/((1+discount)^hiv_trt_ly$nyr[i]))
  }
  
  hiv_trt_qaly[hiv_trt_qaly$Time < 2018, 3:54] <- 0
  
  hiv_trt_qaly$totalQALY <- rowSums(hiv_trt_qaly[,3:54])
  
  return(hiv_trt_qaly)
}

# LIFE YEARS (LY)-------------------------------------------------------------
lima_ref_ly <- GetPersonTime(lima_ref) 

lima_int_ly <- GetPersonTime(lima_int)

# QALYs discounted-------------------------------------------------------------
lima_ref_qaly <- GetQALYs(lima_ref_ly)

lima_int_qaly  <- GetQALYs(lima_int_ly)
```

We calculate the total life years (LYs) and quality-adjusted life years (QALYs).

## Costs

We convert all costs from 2011 soles to 2017 soles, then exchange to USD 2017 using the 
consumer price index. 

```{r cost functions}

# FUNCTIONS FOR COSTS --------------------------------------------------------------------

GetCostParams <- function(prob = FALSE, nsims, cAcuteDx, cpi = cpi, societal = FALSE){
  # Generate the set of cost parameters and input values for the HIV cost-effectiveness 
  #      analysis. Create probabilistic draws from the distribution of uncertainty around each cost. 
  # 
  # Arguments:
  #   @prob: logical indicator of the simulation being deterministic or probabilistic
  #   @nsims: number of simulations if probabilistic otherwise 1
  #   @cAcuteDx: cost (US$) of acute diagnosis in the Sabes study
  #   @cpi: table of consumer price index from loaded .csv file
  #   @societal: logical indicator for the analysis perspective, default is payer
  # 
  # Returns: 
  #     Dataframe with nsims number of values for each of the 64 cost parameters (2017 US$)
  
  cAcuteDx <- cAcuteDx   # THE COST OF DIAGNOSIS

  # Note that "S/" means "soles"
  # some parts of diagnosis are different with the SABES intervention
  # no intervention diagnosis cost: regular testing costs + 1yr high personelle costs
  # SABES acutes diagnosis cost: [SABES cost per acute diagnosed] + [SABES linkage to care] 
  #     + 1 yr of high personelle costs
  # SABES non-acute diagnosis: [previous testing to get them diagnosed] * 
  #     (1-P(SABES_coverage|nonAcute)) + [linkage to care] + 1 yr of high personelle costs
  
  cRegularDx <- (
    1467*cpi$X2016[1]/cpi$X2014[1] + # 2014 soles per HIV diagnosis in the control group
    12.06*12*cpi$X2016[1]/cpi$X2014[1]  # USD 2014 (physician, nurse) personelle costs in first year
    ) 
  
  # Cost based on level of engagment in care (2016 USD)
  cTreat <- (
    92.68*3*cpi$X2016[1]/cpi$X2010[1] + # quarterly cost of HIV treatment (inflated from 2010)
    41.5*3*cpi$X2016[1]/cpi$X2015[1]  + # quarterly cost of labs during HIV treatment (>1 yr post-diagnosis)
    4.62*3*cpi$X2016[1]/cpi$X2014[1] # personelle costs per quarter
  )

  # quarterly costs
  # only U and T are on ART
  c.SL   <- 0
  c.SH    <- 0
  c.SPL   <- 0
  c.SPH <- 0
  c.I1L <- 0
  c.I1H <- 0
  c.I2L <- 0
  c.I2H <- 0
  c.I3L <- 0
  c.I3H <- 0
  c.I4L <- 0
  c.I4H <- 0
  c.I5L <- 0
  c.I5H <- 0
  c.D1L <- 0
  c.D1H <- 0
  c.D2L <- 0
  c.D2H <- 0
  c.D3L <- 0
  c.D3H <- 0
  c.D4L <- 0
  c.D4H <- 0
  c.D5L <- 0
  c.D5H <- 0
  c.E1L <- 0
  c.E1H <- 0
  c.E2L <- 0
  c.E2H <- 0
  c.E3L <- 0
  c.E3H <- 0
  c.E4L <- 0
  c.E4H <- 0
  c.E5L <- 0
  c.E5H <- 0
  c.U1L <- cTreat
  c.U1H <- cTreat
  c.U2L <- cTreat
  c.U2H <- cTreat
  c.U3L <- cTreat
  c.U3H <- cTreat
  c.U4L <- cTreat
  c.U4H <- cTreat
  c.U5L <- cTreat
  c.U5H <- cTreat
  c.T1L <- cTreat
  c.T1H <- cTreat
  c.T2L <- cTreat
  c.T2H <- cTreat
  c.T3L <- cTreat
  c.T3H <- cTreat
  c.T4L <- cTreat
  c.T4H <- cTreat
  c.T5L <- cTreat
  c.T5H <- cTreat
  c.NewI  <- 0
  c.NewA  <- 0
  c.NewD1 <- 0
  c.NewD2 <- 0
  c.NewD3 <- 0
  c.NewD4 <- 0
  c.NewD5 <- 0
  c.Deaths <- 0
  c.AcuteDx <- cAcuteDx
  c.RegularDx <- cRegularDx
  
  
  for (i in 1: nsims){
    
    C <- c( c.SL[i], c.SH[i], c.SPL[i],c.SPH[i],
            c.I1L[i], c.I1H[i], c.I2L[i], c.I2H[i], c.I3L[i], c.I3H[i], c.I4L[i], c.I4H[i], c.I5L[i], c.I5H[i], 
            c.D1L[i], c.D1H[i], c.D2L[i], c.D2H[i], c.D3L[i], c.D3H[i], c.D4L[i], c.D4H[i], c.D5L[i], c.D5H[i], 
            c.E1L[i], c.E1H[i], c.E2L[i], c.E2H[i], c.E3L[i], c.E3H[i], c.E4L[i], c.E4H[i], c.E5L[i], c.E5H[i], 
            c.U1L[i], c.U1H[i], c.U2L[i], c.U2H[i], c.U3L[i], c.U3H[i], c.U4L[i], c.U4H[i], c.U5L[i], c.U5H[i], 
            c.T1L[i], c.T1H[i], c.T2L[i], c.T2H[i], c.T3L[i], c.T3H[i], c.T4L[i], c.T4H[i], c.T5L[i], c.T5H[i], 
            c.NewI[i], c.NewA[i], c.NewD1[i], c.NewD2[i], c.NewD3[i], c.NewD4[i], c.NewD5[i], c.Deaths[i], 
            c.AcuteDx[i], c.RegularDx[i])
  }
  
  return(as.matrix(C))
}

CostingCalc <- function(hiv_trt_ly, C){
  # Apply costs to the health state outcomes from the dynamic transmission model
  #
  # Args:
  #   @hiv_trt_ly: table with scenario life years in each health state for each quarter in analysis time horizon
  #   @C: table of cost input parameters and values to apply to time in health states
  #
  # Returns: 
  #   Table of costs for each health state each quarter of the analysis time horizon
  
  hiv_trt_cost <- hiv_trt_ly
  
  hiv_trt_cost[3:c(2+length(C))] <- NA
  
  for(i in 1:nrow(hiv_trt_ly)){
    hiv_trt_cost[i,3:c(2+length(C))] <- hiv_trt_ly[i,3:c(2+length(C))] * C * (1/((1+discount)^hiv_trt_ly$nyr[i]))
  }
  
  hiv_trt_cost$totalCostHIVcare <- rowSums(hiv_trt_cost[,5:54])
  
  hiv_trt_cost$totalCost <- rowSums(hiv_trt_cost[,3:c(2+length(C))])
  
  return(hiv_trt_cost)
}

# assign the cost parameter values for each health state
C <- GetCostParams(prob = FALSE, nsims = 1, cpi = cpi, cAcuteDx = cAcuteDx, societal = FALSE)

n_C_params <- length(C) # number of cost parameters used in the analysis

lima_ref_cost <- CostingCalc(lima_ref_ly, C) # reference group costs

lima_int_cost <- CostingCalc(lima_int_ly, C) # intervention costs
```

<br>

# Cost-Effectiveness

We apply a cost-effectiveness threshold of 3 x per capita gross domestic product for Peru in 2017.

```{r cost effectiveness}
# merge the reference group outcomes (.x) with the intervention outcomes (.y)

ly <-  lima_ref_ly %>%
  left_join(lima_int_ly, by = 'X') 

qaly <- lima_ref_qaly %>%
  left_join(lima_int_qaly, by = 'X')

cost <-  lima_ref_cost %>%
  left_join(lima_int_cost, by = 'X')

result_cost <- cost %>%
  summarise(outcome = "Cost",
            total_ref = scales::dollar(sum(totalCost.x)),
            total_int = scales::dollar(sum(totalCost.y)),
            inc = scales::dollar(sum(totalCost.y) - sum(totalCost.x)),
            total_ref_pp = scales::dollar(sum(totalCost.x)/pp_n),
            total_int_pp = scales::dollar(sum(totalCost.y)/pp_n),
            inc_pp = scales::dollar((sum(totalCost.y) - sum(totalCost.x))/pp_n)
            )

result_qaly <- qaly %>%
  summarise(outcome = "QALYs",
            total_ref = scales::comma(sum(totalQALY.x), digits = 0),
            total_int = scales::comma(sum(totalQALY.y), digits = 0),
            inc = scales::comma(sum(totalQALY.y) - sum(totalQALY.x), digits = 0),
            total_ref_pp = round(sum(totalQALY.x)/pp_n, digits = 3),
            total_int_pp = round(sum(totalQALY.y)/pp_n,  digits = 3),
            inc_pp = round((sum(totalQALY.y) - sum(totalQALY.x))/pp_n,  digits = 3)
            )

result_infection <- qaly %>%
  summarise(outcome = "HIV Infections",
            total_ref = scales::comma(max(NewI.x) - min(NewI.x), digits = 0),
            total_int = scales::comma(max(NewI.y) - min(NewI.y), digits = 0),
            inc = scales::comma(max(NewI.y) - min(NewI.y) - (max(NewI.x) - min(NewI.x)), digits = 0),
            total_ref_pp = scales::comma((max(NewI.x) - min(NewI.x))/pp_n, digits = 3),
            total_int_pp = scales::comma((max(NewI.y) - min(NewI.y))/pp_n, digits = 3),
            inc_pp = scales::comma((max(NewI.y) - min(NewI.y) - (max(NewI.x) - min(NewI.x)))/pp_n, digits = 3)
            )

results <- rbind(result_infection, result_qaly, result_cost)

htmlTable(results)

```


```{r icer calc}
icer <- (sum(cost$totalCost.y) - sum(cost$totalCost.x)) /
                       (sum(qaly$totalQALY.y) - sum(qaly$totalQALY.x)
                       )
```

<br>

The incremental cost-effectiveness ratio (ICER) for the SABES program was `r scales::dollar(icer)` 
per QALY gained. Given our assumed a cost-effectiveness threshold of `r scales::dollar(threshold)` 
per QALY gained (1xGDP per capita for Lima in 2017), we found this intervention to be cost-effective. 

<br>
